---
title: "Basic_Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic_Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

# Crossdome - Biochemical properties predictions

## Performing Crossdome screening

```{r loading, warning = FALSE}

library(crossdome)

database <- cross_background(off_targets = 'ESDPIVAQY', allele = "HLA-A*01:01")
result <- cross_compose(query = 'EVDPIGHLY', background = database)

```

```{r structure}

str(result)

```

## Generating mRNA expression heatmap 

```{r expression, fig.height = 10, fig.width = 10, paged.print = TRUE}

result <- cross_expression_matrix(result, pvalue_threshold = 0.005)
cross_expression_plot(object = result)

```

The heatmaps consider the peptide-donors expression across healthy tissues from **Human Protein Atlas**. Crossdome provides the HPA data through the function `data("hpa_database")`. Additionally, the peptide-donor mapping can be inspected on the `result@expression` slot. 

## Summarising tissue specificity across candidates

```{r tissue_spec, fig.height = 4, fig.width = 6.5}

cross_tissues_plot(object = result)


```

## Displaying peptide composition across best-score candidates

```{r substitution, fig.height = 12, fig.width = 6.5, paged.print = TRUE}

result <- cross_substitution_matrix(result)
cross_substitution_plot(object = result)

```

```{r}

if(FALSE) {
  
      cross_write(result, file = "/tmp/crossdome_results.tsv")
  
}

```
